CS378: Final Project - Data Artifacts \\ \url{https://github.com/sarimaleem/cs378_fp}

### 2023-04-27 paper/main.tex
some changes, time to review the paper lmao

For the fix, we took ambiguous data from the first 50000 training examples and
trained on those for 15 epochs.

\todo{Describe the task/dataset/model you are working on. Clearly define your
task with mathematical notations. Describe your learning algorithm. You must
formally specify the loss function, stopping criteria, training data, etc used
for the model you are analyzing in the next section. Remember, every notation
you use must be defined.}

>>>>

For the fix, we took 1655 ambiguous data examples from the first 50000 training
examples and trained on those for 15 epochs on top of the original model. We
also trained 6915 difficult to learn examples for 5 epochs on top of the
baseline model and evaluate that.
